Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-06-23 doc/main_jfm.tex
updates

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.8\textwidth]{Slip.eps}
\end{center} 
  \caption{For a high shear rate $\dot\gamma=0.005$, the inter-monolayer slip is be observed. 
  }
    \label{figure5}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{N58_parabolic.eps}
  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$ and the control parameter $w=10$. The configuration is the state when $t=20000$.
  }
    \label{figure6}
\end{figure}

>>>>

An interesting phenomenon also rises up in the proposed setup where the inter-monolayer slip occurs 
between two leaflets. When a shear rate is large enough, take $\dot\gamma = 0.005$ as an example, 
Figure~\ref{figure5} shows the schematic of the test. A particle pair is initially marked and we then track the positions and layer velocities over the time. It is clear to see that the outer leaflet always has larger 
tangential velocity than the one from inner leaflet. This inter-leaflet sliding matches what has been seen
in articles in molecular dynamics simulations. %%% need some citations

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.8\textwidth]{Slip.eps}
\end{center} 
  \caption{For the shear rate $\dot\gamma=0.005$, the inter-monolayer slip is be observed. The curves in black and blue represent the tangential velocities of inner and outer leaflet, respectively. The configuration plots have two fixed particles marked and positioned with respect to the corresponding time $t$.
  }
    \label{figure5}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{N58_parabolic.pdf}
  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$ and the control parameter $w=10$. The configuration is the state when $t=20000$.
  }
    \label{figure6}
\end{figure}
